sensitivity

### 2023-06-02 scripts/workshop/sensitivity.Rmd
Update sensitivity.Rmd

```{r library, message = F}
library(tidyverse)
library(magrittr)
#install_github("thomasp85/patchwork")
library(patchwork)
library(ggnewscale)
library(here)
library(deSolve)
```

@@

```{r lhs}
h <- 1000               #choose number of points
set.seed(8878896)
lhs<-maximinLHS(h,6)   #simulate
```

```{r}
mu_a_min <- 1/50
mu_a_max <- 1/50
mu_b_min <- 1/50
mu_b_max <- 1/50
beta_min <- 0.001
beta_max <- 0.001
betab_min <- 0.0001
betab_max <- 0.0001
phi_min <- 0.001
phi_max <- 0.001
lambda_min <- 5/3
lambda_max <- 5/3
alpha_min <- 1/10
alpha_max <- 1/10
sigma_min <- 1/2
sigma_max <- 1/2
epsilon_min <- 1/2
epsilon_max <- 1/2

params.set <- cbind(
  mu_a <- lhs[,1]*(mu_a_max - mu_a_min) + mu_a_min,
  mu_b <- lhs[,2]*(mu_b_max - mu_b_min) + mu_b_min,
  beta <- lhs[,3]*(beta_max - beta_min) + beta_min,
  betab <- lhs[,4]*(betab_max - betab_min) + betab_min,
  phi <- lhs[,5]*(phi_max - phi_min) + phi_min,
  lambda <- lhs[,6]*(lambda_max - lambda_min) + lambda_min,
  alpha <- lhs[,7]*(alpha_max - alpha_min) + alpha_min,
  sigma <- lhs[,8]*(sigma_max - sigma_min) + sigma_min,
  epsilon <- lhs[,9]*(epsilon_max - epsilon_min) + epsilon_min,
)

@@

```{r}

>>>>

```{r library, message = F}
library(tidyverse)
library(magrittr)
#install_github("thomasp85/patchwork")
library(patchwork)
library(ggnewscale)
library(here)
library(deSolve)
library(lhs)
```

@@

```{r lhs}
h <- 1000               #choose number of points
set.seed(8878896)
lhs<-maximinLHS(h,9)   #simulate
```

```{r}
mu_a_min <- 1/50*0.8
mu_a_max <- 1/50*1.2
mu_b_min <- 1/50*0.8
mu_b_max <- 1/50*1.2
beta_min <- 0.001*0.8
beta_max <- 0.001*1.2
betab_min <- 0.0001*0.8
betab_max <- 0.0001*1.2
phi_min <- 0.001*0.8
phi_max <- 0.001*1.2
lambda_min <- 5/3*0.8
lambda_max <- 5/3*1.2
alpha_min <- 1/10*0.8
alpha_max <- 1/10*1.2
sigma_min <- 1/2*0.8
sigma_max <- 1/2*1.2
epsilon_min <- 1/2*0.8
epsilon_max <- 1/2*1.2

params.set <- cbind(
  mu_a <- lhs[,1]*(mu_a_max - mu_a_min) + mu_a_min,
  mu_b <- lhs[,2]*(mu_b_max - mu_b_min) + mu_b_min,
  beta <- lhs[,3]*(beta_max - beta_min) + beta_min,
  betab <- lhs[,4]*(betab_max - betab_min) + betab_min,
  phi <- lhs[,5]*(phi_max - phi_min) + phi_min,
  lambda <- lhs[,6]*(lambda_max - lambda_min) + lambda_min,
  alpha <- lhs[,7]*(alpha_max - alpha_min) + alpha_min,
  sigma <- lhs[,8]*(sigma_max - sigma_min) + sigma_min,
  epsilon <- lhs[,9]*(epsilon_max - epsilon_min) + epsilon_min
)

@@

```{r}
levels <- 11

h2 <- 250

j <- 1

data <- data.frame(matrix(rep(NA,levels*h2*14),nrow=levels*h2))
for(i in 1:h2){

    data[j,1:9] <- as.list(c(params.set[i,]))
    params <- params.set[i,]
    out <- as.data.frame(lsoda(xstart, times, rm0, params))
    data[j,10] <- tail(out$Ia, 1)
    data[k,11] <- tail(out$Ib, 1)s
    j <- j+1

}
```
